## This is my first homework assignment

---
title: "Homework 1"
author: Amanda Kramer (on Charles Biggar's computer)
output: github_document
---

This is my HW1: (Problem 1.0 done while working together in class)

```{r}
library(tidyverse)
```

##Problem 0.1


## Problem 1

Create a data frame with the specified elements. 

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor. 

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```


why don't i like `$` : Dr. Goldsmith

```{r no_dollars}
prob1_df$samp
pull(prob1_df, samp)
prob1_df[["samp"]]
```


# Problem 2.0

#install package in console

data("penguins", package = "palmerpenguins")

```{r homework_1_pr2}
library(tidyverse)

