
---
title: "Homework 1"
author: Amanda Kramer (on Charles Biggar's computer)
output: github_document
---

This is my HW1: (Problem 1.0 done while working together in class)

#please note: There was a lot of trial in error due to my computer crashing and requiring redownloading/configuring R on my boyfriend's laptop. Please refer to my emails with Dr. Goldsmith.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements. 

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor. 

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```


"why don't i like `$`" : Dr. Goldsmith

```{r no_dollars}
prob1_df$samp
pull(prob1_df, samp)
prob1_df[["samp"]]
```


# Problem 2.0
#installed package in console
```{r}
data("penguins", package = "palmerpenguins")
```


```{r homework_1_pr2}
library(tidyverse)

hw_df= tibble(

  names(penguins),
  ls(penguins),
  nrow(penguins),
  ncol(penguins)
  )

print(hw_df)
```


Penguins is a dataframe with 8 columns and 344 rows. The variables are "species", "island", "bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g", "sex", "year". The mean flipper length is 200.9152 mm.

#the size of the dataset (using nrow and ncol)
The dataset includes 8 columns and 344 rows

#the mean flipper length
200.9152 


```{r homework_1_pr2_p2}

fl_mean = colMeans(penguins[,5], na.rm = TRUE, dims=1L)
print(fl_mean)


penguins_plot = ggplot(penguins, aes(x=bill_length_mm, y = flipper_length_mm, color= species)) + geom_point()

ggsave(file = "penguins.png")

```


